A Spatial Model of Bus Ridership

### 2020-06-16 report/honors-translation.Rmd
all img to report

@@

### Median Household Income -> income brackets?

@@

### Median Age -> age cohort

@@

@@

@@

@@

@@

@@

@@

### Households with No Vehicle -> number of vehicles per household

@@

### Employment Rate

### Median Gross Rent

### Public Benefits

@@

@@

@@

@@

>>>>

![](/Users/raven/Documents/honors/honors-project/img/map/log_pop_density.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/perc_rent.png){#id .class width=5.75in height=5.11in}

### Median Household Income

![](/Users/raven/Documents/honors/honors-project/img/map/estimate_median_hh_income.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/log_emp_dens.png){#id .class width=5.75in height=5.11in}

### Age Cohorts

@@

![](/Users/raven/Documents/honors/honors-project/img/map/genz.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/millenial.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/genx.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/boomer.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/w_perc_jobs_white.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/w_perc_jobs_age_less30.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/walkability.png){#id .class width=5.75in height=5.11in}

### Average Number of Vehicles per Household

![](/Users/raven/Documents/honors/honors-project/img/map/avg_veh.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/perc_wfh.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/college.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/lightrail.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/airport.png){#id .class width=5.75in height=5.11in}

@@

![](/Users/raven/Documents/honors/honors-project/img/map/hospital.png){#id .class width=5.75in height=5.11in}
